Giant Low Surface Brightness Galaxies As Merger Remnants

### 2016-06-01 glsb.tex
printing out
cleaning out xxx's

\shorttitle{Short Title}
\shortauthors{Yoachim et al.}

@@

In comparison, the stellar disk of Malin~2 extends beyond 40 kpc (5.9 $R_e$), and the HI disk reaches beyond 100 kpc (14.8 $R_e$).  These distances have occasionally been reached by x-ray observations \citep{Buote12}.

@@

%The problem with considering GLSB systems as normal spirals is that they are clearly outliers when one considers the specific angular momentum of the systems.  The difference between high surface brightness (HSB) spirals and low surface brightness spirals (LSB), could simply be an issue of specific angular momentum. xxx-this goes in the discussion I think. \citet{Dutton12} is a nice paper on how disk galaxies get their angular momentum--I'll need to make a calc of how much J is in the GLSB disks to compare it.

@@

XXX-\citet{Kasparova14} has an amazing analysis of Malin 2.  They combine ARC photometry, DIS spectra, and Gemini spectra to mass-model the system.  They find the broadband colors are not consistent with a catastrophic formation, but are best fit by exponentially declining SFH.  They think the main difference between Malin~2 and non-giant LSB galaxies is the dark matter halo scale.  I think this is begging the question a little bit

\citet{Galaz15} take deep images of Malin~1 and find the stellar disk extends to 160 kpc.

@@

%XXX-need to look up some Thilker papers on extended UV disks, since these objects could be similar.  From his talk, UGC 1382 shows up in stripe 82 coadd (and NUV).  UGC 3642, GALEX shows a disk, and \HI\ is counter rotating.

@@

%Observations were made using the Dual Imaging Spectrograph (DIS) on
%the ARC 3.5 meter telescope at Apache Point Observatory (APO).  Malin 2 was observed on 4/01/13, and UGC 06614 was observed 5/01/13.  Both galaxies were observed with the XXX gratings and multiple positions of the 1.5\arcsec\ slit.
%XXX-insert table with galaxy name, position, total exposure time
%XXX-insert figure showing slit positions overlayed on the SDSS thumbnails.

@@

%XXX-crap, whatever happened to the gas kinematics?  There are emission lines out there--are they bright enough to get in single fibers of not?  Looks like for Malin 2 the emission lines are only coming from one side of the galaxy.  UGC 6614 is mostly emission from the center.

@@

%XXX-It would be great to get high resolution \HI\ observations of these systems since they could probably be higher spatial resolution.

XXX--We are currently observing higher spatial resolution IFU data with Gemini (GN-2015A-Q-75) of the central region of these galaxies to confirm they are normal elliptical galaxies and to help constrain a more sophisticated dynamical model.

@@

XXX-clearly need to look up bulge-to-disk metallicity gradient.  Lauren did it with colors in \citet{MacArthur04}.  Nice look with metallicity gradients as a function of scale-length, and kpc, and vrot and galaxy type.  Did spectra gradients in \citet{MacArthur09}.  MANGA would make this easy to compare...Maybe there's a SAURON paper on metallicity gradients.

While the old stellar populations in the disks is evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.  Since modern photometric surveys are often surface brightness limited, it is possible a gLSB system will be found in the future that is descended from a collisional ring.

@@

In a future work, we plan to combine our IFU observations with higher spatial resolution long-slit spectra from the Apache Point 3.5m telescope to determine if the central ellipticals are dynamically distinct from their disks.

@@

%\begin{figure}
%\plottwo{Plots/sellarv_trimmed_malin2.eps}{Plots/rc_malin2.eps} \\
%\plottwo{Plots/binned_stelv_trimmed_malin2.eps}{Plots/binned_rc_trimmed_malin2.eps}
%\caption{Fitted rotation curve after clipping outliers for the stellar velocity maps and the binned maps.}
%\end{figure}
%XXX-do an actual tilted ring fit to this shit.

@@

%\begin{figure}
%\plottwo{Plots/rsfr_ebUGC06614.eps}{Plots/rel_ebUGC06614.eps}
%\caption{The best fitting star formation histories and resulting total stellar mass fractions.   For all radial bins, the stellar mass is dominated by stars older than 2 Gyr.  Error bars represent the best XXX fitting models.  \label{sfh_ugc} }
%\end{figure}

>>>>

\shorttitle{GLSB as Merger Remnants}
\shortauthors{Yoachim et al.}

@@

In comparison, the stellar disk of Malin~2 extends beyond 40 kpc (5.9 $R_e$), and the HI disk reaches beyond 100 kpc (14.8 $R_e$).  \citet{Galaz15} take deep images of Malin~1 and find the stellar disk extends to 160 kpc.  These distances have occasionally been reached by x-ray observations \citep{Buote12}.

@@

%The problem with considering GLSB systems as normal spirals is that they are clearly outliers when one considers the specific angular momentum of the systems.  The difference between high surface brightness (HSB) spirals and low surface brightness spirals (LSB), could simply be an issue of specific angular momentum. -this goes in the discussion I think. \citet{Dutton12} is a nice paper on how disk galaxies get their angular momentum--I'll need to make a calc of how much J is in the GLSB disks to compare it.

@@

In one of the most extensive studies of a gLSB system, \citet{Kasparova14} combine ARC 3.5m photometry and long-slit spectra with Gemini spectra to mass-model Malin~2.  They find the broadband colors are not consistent with a catastrophic formation, but are best fit by exponentially declining SFH.  They speculate the main difference between Malin~2 and non-giant LSB galaxies is the dark matter halo scale.  To some extent, this is not a particularly satisfying conclusion because one is then left with the mystery of why Malin~2's dark matter halo is so different from non-giant galaxies.

@@

%-need to look up some Thilker papers on extended UV disks, since these objects could be similar.  From his talk, UGC 1382 shows up in stripe 82 coadd (and NUV).  UGC 3642, GALEX shows a disk, and \HI\ is counter rotating.

@@

%Observations were made using the Dual Imaging Spectrograph (DIS) on
%the ARC 3.5 meter telescope at Apache Point Observatory (APO).  Malin 2 was observed on 4/01/13, and UGC 06614 was observed 5/01/13.  Both galaxies were observed with the  gratings and multiple positions of the 1.5\arcsec\ slit.
%-insert table with galaxy name, position, total exposure time
%-insert figure showing slit positions overlayed on the SDSS thumbnails.

@@

%-crap, whatever happened to the gas kinematics?  There are emission lines out there--are they bright enough to get in single fibers of not?  Looks like for Malin 2 the emission lines are only coming from one side of the galaxy.  UGC 6614 is mostly emission from the center.

@@

%-It would be great to get high resolution \HI\ observations of these systems since they could probably be higher spatial resolution.

@@

One of the most important features we can see in our data is the sharp metallicity gradient as one transitions between the central region and the disk in both Malin~2 and UGC~6614 (Figures~\ref{metal_malin2} and~\ref{metal_ugc}).  For both galaxies, the best fitting star formation histories show the stellar populations are dominated by old stars inside and outside the transition, but the metallicity changes by $\sim0.7-1.0$ dex.  This is a very sharp gradient compared to what has been found in normal spirals for the bulge-to-disk transition region.  \citet{MacArthur04} spectroscopically observed a range of spiral galaxies and found the metallicity profiles which were dropping, rising, and flat.  Using braidband colors, \citet{MacArthur04} also found metallicity gradients of $\sim0$\ to $-0.1$ dex kpc$^{-1}$, at least a factor of two less than what we observe in Malin~2. Also note that our metallicity gradient could be an underestimate of the true gradient since the central metallicities are at the limits of our model grid, and we have spatially binned data, possibly washing out how sharp the transition is.

While the old stellar populations in the disks of Malin~2 and UGC~6614 are evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.  Since modern photometric surveys are often surface brightness limited, it is possible a gLSB system will be found in the future that is the decendent of a collisional ring system.

@@

We are currently observing higher spatial resolution IFU data with Gemini (GN-2015A-Q-75) of the central region of these galaxies to confirm they are normal elliptical galaxies and to help constrain a more sophisticated dynamical model.

@@

%\begin{figure}
%\plottwo{Plots/sellarv_trimmed_malin2.eps}{Plots/rc_malin2.eps} \\
%\plottwo{Plots/binned_stelv_trimmed_malin2.eps}{Plots/binned_rc_trimmed_malin2.eps}
%\caption{Fitted rotation curve after clipping outliers for the stellar velocity maps and the binned maps.}
%\end{figure}
%do an actual tilted ring fit to this shit.

@@

%\begin{figure}
%\plottwo{Plots/rsfr_ebUGC06614.eps}{Plots/rel_ebUGC06614.eps}
%\caption{The best fitting star formation histories and resulting total stellar mass fractions.   For all radial bins, the stellar mass is dominated by stars older than 2 Gyr.  Error bars represent the best fitting models.  \label{sfh_ugc} }
%\end{figure}
